            \subsubsection*{Thermometer Code}

                Next, we'll relax how number-like our feature is. This time, we don't need our data to behave like a number, but it does have an \textbf{ordering}.
                    \note{By "relax", we mean we'll remove some requirements for our feature, like being able to add them together.}

                Some examples:

                \begin{itemize}
                    \item Results of an opinion poll:
                        \begin{itemize}
                            \item "Strongly Agree", "Agree", "Neutral", "Disagree", "Strongly Disagree"
                        \end{itemize}
                    
                    \item Education level: 
                        \begin{itemize}
                            \item "Below High School", "High School Degree", "Associates Degree", "Bachelors" "Advanced Degree"
                        \end{itemize}
                    
                    \item Ranking of athletes
                \end{itemize}

                In this case, we can't just use numbers $\{1,2,3,...\}$. Why not?

                Because that implies that there's a specific "scaling" between points: Is the \#1 athlete twice as good as the \#2 athlete? Maybe, but that's not what the ranking tells us!\\

                \begin{concept}
                    Data that is \vocab{ordered} but not \purp{numerical} cannot be represented with \gren{a single real number}.

                    Otherwise, we might consider one element to be a certain amount "larger" or "smaller" than another, when that's not what \gren{ordering} means.
                \end{concept}

                \miniex Suppose we assign $\{1,2,3\}$ for $\{Disagree, Neutral, Agree\}$. The person who writes 'agree' is doesn't "agree three times as much" as the person who writes 'disagree'!

                But, we still want to keep that ordering: counting up from one element to the next. How do create an order without creating an exact, numeric difference?

                Just now, we tried to count by increasing a single variable. But, there's another way to count: counting up using multiple different variables!
                    \note{This approach is more similar to counting on your fingers.}

                \begin{equation*}
                    \text{Class 1} \longrightarrow
                    \begin{bmatrix}
                        \blu{0} \\ \blu{0} \\ \blu{0} \\ \red{1}
                    \end{bmatrix}
                    \qquad \;\;
                    \text{Class 2} \longrightarrow
                    \begin{bmatrix}
                        \blu{0} \\ \blu{0} \\ \red{1} \\ \red{1}
                    \end{bmatrix}
                    \qquad \;\;
                    \text{Class 3} \longrightarrow
                    \begin{bmatrix}
                        \blu{0} \\ \red{1} \\ \red{1} \\ \red{1}
                    \end{bmatrix}
                    \qquad \;\;
                    \text{Class 4} \longrightarrow
                    \begin{bmatrix}
                        \red{1} \\ \red{1} \\ \red{1} \\ \red{1}
                    \end{bmatrix}
                \end{equation*}
                
                This version allows us to avoid the problems we had before: this doesn't behave the same way as a \textbf{numerical} value.

                To better understand what's going on, here's another way to frame it:
                    \note{Class$(x)$ is just shorthand for, "which class is $x$ in?"}

                \begin{equation}
                    \phi(x) =
                    \begin{bmatrix}
                        \text{Class}(x)\geq 4 \\
                        \text{Class}(x)\geq 3\\
                        \text{Class}(x)\geq 2\\
                        \text{Class}(x)\geq 1
                    \end{bmatrix}
                \end{equation}

                \miniex Suppose $x$ is in class 3. The bottom three statements are all true, the top one is false: so we get $[0, 1, 1, 1]^T$. 

                This helps us understand why this encoding is so useful:
                
                \begin{itemize}
                    \item We aren't directly "adding" variables to each other: they stay separated by \textbf{index}.
                    
                    \item When using a linear model $\theta^T\phi(x)$, each class  matches a different $\theta_i$.
                        \note{$\theta_i$ scales the $\nth{i}$ variable. So, each class can be scaled differently!}
                        
                    \item Despite not behaving like numbers, "higher" classes in the order still keep track of all of the classes below them.
                        \begin{itemize}
                            \item \miniex Class 2-4 all share the feature $\text{Class}(x)\geq 2$ (equivalent to $\text{Class}(x)>1$).
                        \end{itemize}
                \end{itemize}

                This technique is called \textbf{thermometer encoding}.\\

                \begin{definition}
                    \vocab{Thermometer encoding} is a \purp{feature transform} where we take each class and turn it into a feature vector $\phi(x)$ where

                    \begin{equation*}
                    \text{Class 1} \longrightarrow
                    \begin{bmatrix}
                        \blu{0} \\ \vdots \\ \blu{0} \\ \blu{0} \\ \red{1}
                    \end{bmatrix},
                    \qquad 
                    \text{Class 2} \longrightarrow
                    \begin{bmatrix}
                        \blu{0} \\ \vdots \\ \blu{0} \\ \red{1} \\ \red{1}
                    \end{bmatrix}
                    \qquad
                    \text{Class 3} \longrightarrow
                    \begin{bmatrix}
                        \blu{0} \\ \vdots \\ \red{1} \\ \red{1} \\ \red{1}
                    \end{bmatrix}
                    \qquad
                    \text{Class } k \longrightarrow
                    \begin{bmatrix}
                        \red{1} \\ \vdots \\ \red{1} \\ \red{1} \\ \red{1}
                    \end{bmatrix}
                \end{equation*}

                    \begin{itemize}
                        \item The \purp{length of the vector} is the \gren{number of classes} $k$ we have.
                        \item The $\nth{i}$ class has $i$ \purp{ones}.
                    \end{itemize}

                    \phantom{}

                    \begin{itemize}
                        \item This transformation is only appropriate if the data 
                            \begin{itemize}
                                \item Is \purp{ordered},
                                \item But not \gren{real number-compatible}: we can't add the values, or compare the "amount" of each feature.
                            \end{itemize}
                    \end{itemize}
                \end{definition}

                \miniex We reuse our example from earlier: 

                \begin{equation*}
                    \phi(x_{\text{Class 1}}) =
                    \begin{bmatrix}
                        \blu{0} \\ \blu{0} \\ \blu{0} \\ \red{1}
                    \end{bmatrix},
                    \qquad \;\;
                    \phi(x_{\text{Class 2}}) =
                    \begin{bmatrix}
                        \blu{0} \\ \blu{0} \\ \red{1} \\ \red{1}
                    \end{bmatrix}
                    \qquad \;\;
                    \phi(x_{\text{Class 3}}) =
                    \begin{bmatrix}
                        \blu{0} \\ \red{1} \\ \red{1} \\ \red{1}
                    \end{bmatrix}
                    \qquad \;\;
                    \phi(x_{\text{Class 4}}) =
                    \begin{bmatrix}
                        \red{1} \\ \red{1} \\ \red{1} \\ \red{1}
                    \end{bmatrix}
                \end{equation*}

            \subsecdiv
            \subsubsection*{One-hot Code}

                We introduced this technique in the \textbf{previous} chapter:
                
                When there's no clear way to \textbf{simplify} our data, we accept the current discrete classes, and \textbf{convert} them to a number-like form.

                \begin{itemize}
                    \item Examples:
                    \begin{itemize}
                        \item Colors: $\{Red, Orange, Yellow, Green, Blue, Purple\}$
                        \item Animals: $\{Dog, Cat, Bird, Spider, Fish, Scorpion\}$
                        \item Companies: $\{Walmart, Costco, McDonald's, Twitter\}$
                    \end{itemize}
                \end{itemize}

                We can't use thermometer code, because that suggests a natural \textbf{order}. And we definitely can't use real numbers.

                \miniex $\{Brown, Pink, Green\}$ doesn't necessarily have an obvious order: you could force one, but there's no reason to.

                But, we can use one idea from thermometer code: each class in a different variable.
        
                \begin{equation}
                    \begin{bmatrix}
                      C_1\\C_2\\ \vdots \\ C_k
                    \end{bmatrix}
                \end{equation}

                But in this case, we don't "build up" our vector: we replace $\text{Class}(x)\geq 4$ with $\text{Class}(x)= 4$.

                \begin{equation}
                    \phi(x) =
                    \begin{bmatrix}
                        \text{Class}(x) = 4 \\
                        \text{Class}(x) = 3\\
                        \text{Class}(x) = 2\\
                        \text{Class}(x) = 1
                    \end{bmatrix}
                \end{equation}
                
            This approach is called \textbf{one-hot encoding}.\\
            
            \begin{definition}
                \vocab{One-hot encoding} is a way to represent \vocab{discrete} information about a data point.
                
                Our $k$ classes are stored in a length-$k$ column \gren{vector}. For \purp{each} variable in the vector, 
                
                \begin{itemize}
                    \item The value is \gren{0} if our data point is \purp{not in that class}.
                    \item The value is \gren{1} if our data point is \purp{in that class}.
                \end{itemize}

                 \begin{equation*}
                    \text{Class 1} \longrightarrow
                    \begin{bmatrix}
                        \blu{0} \\ \vdots \\ \blu{0} \\ \blu{0} \\ \red{1}
                    \end{bmatrix},
                    \qquad 
                    \text{Class 2} \longrightarrow
                    \begin{bmatrix}
                        \blu{0} \\ \vdots \\ \blu{0} \\ \red{1} \\ \blu{0}
                    \end{bmatrix}
                    \qquad
                    \text{Class 3} \longrightarrow
                    \begin{bmatrix}
                        \blu{0} \\ \vdots \\ \red{1} \\ \blu{0} \\ \blu{0}
                    \end{bmatrix}
                    \qquad
                    \text{Class } k \longrightarrow
                    \begin{bmatrix}
                        \red{1} \\ \vdots \\ \blu{0} \\ \blu{0} \\ \blu{0}
                    \end{bmatrix}
                \end{equation*}
                
                In one-hot encoding, items are \purp{never} labelled as being in \purp{two} classes at the \gren{same time}.

                \begin{itemize}
                    \item This transformation is only appropriate if the data is
                        \begin{itemize}
                            \item Does not have another \purp{structure} we can reduce it to: it's neither like a \gren{real number} nor \gren{ordered}
                            
                            \item We don't have an \gren{alternative} representation that contains more (accurate) information.
                        \end{itemize}
                \end{itemize}
            \end{definition}
            
            \miniex Suppose that we want to classify \textbf{furniture} as table, bed, couch, or chair.
            
            \begin{equation}
                \begin{bmatrix}
                  \text{table} \\ \text{bed} \\ \text{couch} \\ \text{chair} 
                \end{bmatrix}
            \end{equation}
            
            For each class:
            
            \begin{equation}
                y_{chair} = 
                \begin{bmatrix}
                  0\\0\\0\\ \red{1}
                \end{bmatrix}
                \qquad
                y_{table} = 
                \begin{bmatrix}
                  \red{1}\\0\\0\\0
                \end{bmatrix}
                \qquad
                y_{couch} = 
                \begin{bmatrix}
                  0\\0\\\red{1}\\0
                \end{bmatrix}
                \qquad
                y_{bed} = 
                \begin{bmatrix}
                  0\\\red{1}\\0\\0
                \end{bmatrix}
            \end{equation}

            \subsecdiv
            \subsubsection*{One-hot versus Thermometer}

                One common question is, "why can't we use one-hot for ordered data? We could sort the indices so they're in order".

                However, there's a problem with this logic: the computer \textbf{doesn't care} about the order of the variables in an array: it contains no information!

                Why is that? If the vector has an order, shouldn't that \textbf{affect} the model?
                
                Well, remember that our model is represented by 

                \begin{equation}
                    \theta^T x = \sum_i \theta_i x_i
                \end{equation}

                The vector format $\theta^Tx$ is just a way to \textbf{condense} our equation: the ordering goes away when we compute the sum.\\

                \begin{concept}
                    \vocab{Order} of elements in a vector \purp{don't} affect the behavior of our model.

                    This is because a linear model is a \gren{sum}, and sums are the same regardless of \purp{order}.
                \end{concept}

                If our model has the same math regardless of order, then it can't use order information.

                \miniex We'll take a vector, and rearrange it.
                    \note{Despite shuffling, these two equations are equivalent!}

                \begin{equation*}
                    \theta^T \phi(x) = 
                    \begin{bmatrix}
                        \theta_1 & \theta_2 & \theta_3 & \theta_4
                    \end{bmatrix}
                    \begin{bmatrix}
                        0\\1\\0\\0
                    \end{bmatrix}
                    \qquad\longrightarrow\qquad
                    (\theta^T)^* (\phi(x))^* = 
                    \begin{bmatrix}
                        \theta_3 & \theta_1 & \theta_4 & \theta_2
                    \end{bmatrix}
                    \begin{bmatrix}
                        0 \\ 0 \\ 0 \\ 1
                    \end{bmatrix}
                \end{equation*}

                The math is the same, despite changing order: our model knows nothing about ordering.\\

                \begin{clarification}
                    \vocab{One hot encoding} \purp{cannot} encode information about ordering.

                    \vocab{Thermometer encoding} is required to \gren{represent ordered objects}.
                \end{clarification}

                Why is thermometer encoding able to of representing ordering? Let's try shuffling it, too.

                \begin{equation}
                    \theta^T \phi(x) = 
                    \begin{bmatrix}
                        \theta_1 & \theta_2 & \theta_3 & \theta_4
                    \end{bmatrix}
                    \begin{bmatrix}
                        0\\1\\1\\1
                    \end{bmatrix}
                \end{equation}

                \begin{equation}
                    (\theta^T)^* (\phi(x))^* = 
                    \begin{bmatrix}
                        \theta_3 & \theta_1 & \theta_4 & \theta_2
                    \end{bmatrix}
                    \begin{bmatrix}
                        1 \\ 0 \\ 1 \\ 1
                    \end{bmatrix}
                \end{equation}

                Even though we've changed the order, we still know this is the \textbf{third} in the order, because we have \textbf{three} 1's!\\

                \begin{concept}
                    Even though the \gren{order of elements} in a vector \purp{doesn't matter}, we can retrieve the order of \vocab{thermometer coding} based on the \purp{number of 1's in the vector}.
                \end{concept}
            